Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Improved clarity of distinction between different quantifications of galaxy size

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$

We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.

@@

@@

@@

>>>>

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile, $\rhalf,$ and the $r-$band flux ratio of the two components, $\bt,$ giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$

We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}. Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs. ``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$

@@

We reiterate an important distinction drawn in the formulation of our forward modeling approach. In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalf.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalf$ is above or below the median size for a galaxy with total stellar mass $\mstar.$

@@

The results shown in \citet{kravtsov13} simplify our task of parameter space exploration: the assumption that composite galaxy size $\rhalf$ scales in linear proportion to halo radius $\rvir$ gives a qualitatively good description of SDSS data over many orders of magnitude in galaxy mass. In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".

@@

\subsection{Progression from Backwards to Forwards Modeling}
\label{subsec:forwardsmodeling}
